\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}

Mark D. Reid provided maximal freedom as a supervisor.
Bob Williamson was incredibly patient as chairman.
He, and three anonymous reviewers who provided constructive comments that greatly improved this work.  

David Balduzzi was an excellent friend and productive collaborator.
Yiling Chen gave generous advice when I was starting to understand the predictions literature.
Scott Sanner was always thoughtful and methodical in engaging with even my wildest questions and frustrations.


Leo Celi and Rob Stretch where generous in helping me in my attempts to understand decision making in medical practice.
Ben Moran, and Adam Kelly, for the friendship and the many conversations that helped me understand the constructive side of contingent claims.


Rafael Frongillo,Brendan van Rooyen, and Garrett Johnson, for their steady and reasonable friendships.
Daniel Reusche and Raphael Kabo for both their friendship and their help proof reading this.
Alice Hutchings, Brendan Loo Gee, Karina Vennonen, Mitchell Jon Brown, Carolina Brum, Nathan Trachimowicz, Mako Hill, Mika Matsuzaki, Blaine Cook and Natasha Carolan for their incredibly generous hospitality and friendship over these yeas.

Avi Ruderman was an ideal co-conspirator and academic sibling. 
Maja Tampe, Tamar Regev, and Jacinta Torres, Dar\'io Garc\'ia Garc\'ia, Carsten Riechelmmann and Erik Garrison, for the many decisions that they made better, and the countless others were they graciously accepted my unreasonableness. 


